---
title: "Green_Building"
author: 
date: "8/18/2019"
output: 
  md_document:
    variant: markdown_github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readr)
library(dplyr)
green <- read.csv('/Users/CatherineMiao/Desktop/STA380-master/data/greenbuildings.csv') %>% as.tbl
head(green)
green$leasing_rate = (green$leasing_rate * .01)
revenue = (green$Rent * green$leasing_rate)
green$Revenue = revenue
```
# class a buildings tend to be larger in size and greener 
```{r}
library(ggplot2)
ggplot(data = green)+
  geom_point(mapping = aes(x=size, y=Revenue, color=green_rating))+
  facet_wrap(~ class_a)
```
# From the density plot, we identify that green buildings tend to have more stories. 
```{r}
ggplot(green) + 
  geom_histogram(aes(x=stories, y=stat(density)), binwidth=2) + 
  facet_grid(green_rating~.)

```
# The density plot shows that green buildings which are 5 years old and younger tend to have more stories than non-green buildings 
```{r}
library(dplyr)
green123 = green %>%
  filter(age <6) 

ggplot(green123) + 
  geom_histogram(aes(x=stories, y=stat(density)), binwidth=2,fill="orange") + 
  facet_grid(green_rating~.)#+ scale_fill_gradient("density", low="green", high="red")

```

# Green buildings are better clustered than non-green buildings 
```{r}
attach(green)
ggplot(green) + 
  geom_histogram(aes(x=cluster, y=stat(density)), binwidth=2) + 
  facet_grid(green_rating~.)

```

```{r}
greenbuildings <- read.csv('/Users/CatherineMiao/Desktop/STA380-master/data/greenbuildings.csv') %>% as.tbl

greenbuildings$Revenue = revenue
greenbuildings$leasing_rate = (greenbuildings$leasing_rate * .01)
revenue = (greenbuildings$Rent * greenbuildings$leasing_rate)
```

# Income Porjection 
# In the 10-year project, both green and nongreen buildings have negative incomes 
```{r}
total_green2 = ((((36.86412*250000)*10)-5000000)/1000000) 
total_nongreen2 = (((22.17286*250000)*10)/1000000) 
GreenBuilding = (total_green2)
NonGreenBuilding = (total_nongreen2)
NonGreenCost = 100
GreenCost = 105
df = data.frame(Years=c(10),NonGreenBuilding, GreenBuilding, GreenCost, NonGreenCost)
Income1= GreenBuilding-GreenCost
Income2 =NonGreenBuilding-NonGreenCost
x <- data.frame("Green" = c("Green", "Non-Green"), "Dollar" = c(105,100,-17.8397, -44.56785), "Revenue" = c("Total Expense","Total Expense","Income","Income"), stringsAsFactors = FALSE)
x
ggplot(data = x, aes(x = x$Green, y =x$Dollar, fill = x$Revenue)) + 
    geom_bar(stat="identity")+ coord_flip() +ggtitle('10 Year Revenue Projection')
```

# In the 15-year Projection, the income for green buildings becomes positive, but the income for non-green buildings are still negative 
```{r}
total_green3 = ((((36.86412*250000)*15)-5000000)/1000000) 
total_nongreen3 = (((22.17286*250000)*15)/1000000) 
GreenBuilding = (total_green3)
NonGreenBuilding = (total_nongreen3)
NonGreenCost = 100
GreenCost = 105
df = data.frame(Years=c(15),NonGreenBuilding, GreenBuilding, GreenCost, NonGreenCost)
Income1 = GreenBuilding - GreenCost 
Income2 = NonGreenBuilding - NonGreenCost
x <- data.frame("Green" = c("Green", "Non-Green"), "Dollar" = c(105,100,28.24045, -16.85178), "Revenue" = c("Total Expense","Total Expense","Income","Income"), stringsAsFactors = FALSE)
x
ggplot(data = x, aes(x = x$Green, y =x$Dollar, fill = x$Revenue)) + 
    geom_bar(stat="identity")+ coord_flip() +ggtitle('15 Year Revenue Projection')


```

# In the 20-year Projection, the income for green buildings largely exceeds non-green buildings 
```{r}
total_green = ((((36.86412*250000)*20)-5000000)/1000000) 
total_nongreen = (((22.17286*250000)*20)/1000000) 
GreenBuilding = (total_green)
NonGreenBuilding = (total_nongreen)
x <- data.frame("Green" = c("Green", "Non-Green"), "Dollar" = c(105,100,74, 11), "Revenue" = c("Total Expense","Total Expense","Income","Income"), stringsAsFactors = FALSE)
x
ggplot(data = x, aes(x = x$Green, y =x$Dollar, fill = x$Revenue)) + 
    geom_bar(stat="identity")+ coord_flip() +ggtitle('20 Year Revenue Projection')#+scale_fill_brewer(palette = 11)
```







