---
title: "R_HW2"
output: 
  pdf_document:
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Key summary

There have been arguments about building a 'safer' portfolio. By 'safer,' we mean the portfolio is less volatile. The following are some of the most common ideas.

**1. Hedge Funds is safer**

Professional fund managers actively manage hedge Funds, and some people believe that makes it 'safer' to invest in a hedge fund because these fund managers have skills and knowledge to prevent the fund from suffering colossal loss.

We use ETFs that track hedge fund's investments to build our portfolio. We picked top 10 (by total assets) ETFs that are categorized in hedge funds from eftdb.co. Then select 5 ETFs that have 5-year data to run our simulation. 

The hedge fund portfolio has a 20-day 5% VaR of around USD 3,000. 


**2. Real Estate is safer**

A lot of people think real estate investment is safer because the market value of real estate assets doesn't change all the time as the stock market does. Thus, we built a portfolio using five real-estate ETFs. However, it turned out the portfolio has a 20-day 5% VaR of around USD 6,500. It's two times as the VaR of the hedge fund portfolio.

**3. Fixed-income securities and stocks**

Some say we should diversify the portfolio by investing in different types of security to make it less volatile. We created a portfolio that consists of three stock ETFs and two fixed-income ETFs. The VaR is about the same level as the real-estate portfolio. 


### set library and functions

```{r, message=FALSE}
library(mosaic)
library(quantmod)
library(foreach)

get_allreturn <- function(usesymbols){
  # get 5-years data
  for( i in c(1:length(usesymbols))){ 
    usesymbols[[i]] = usesymbols[[i]][index(usesymbols[[i]]) >= startdate]
  }
  
  # for( i in c(1:length(usesymbols))){ 
  #   print(head(usesymbols[[i]])) 
  # }
  
  # Combine close to close changes in a single matrix
  all_returns = NULL
  for( i in c(1:length(usesymbols))){ 
    if(is.null(all_returns)){
      all_returns = ClCl(usesymbols[[i]])
    } else {
      all_returns = cbind(all_returns, ClCl(usesymbols[[i]]))
    }
  }
  names(all_returns) = paste0(usesymbolsnames, '.ClCl')
  all_returns = as.matrix(na.omit(all_returns))
  
  return(all_returns)
}

get_sim1 <- function(all_returns, 
                     initial_wealth = 10000, 
                     nsim=5000, 
                     weights = c(0.2, 0.2, 0.2, 0.2, 0.2), 
                     n_days = 20)
{
  sim1 = foreach(i=1:nsim, .combine='rbind') %do% {
  	total_wealth = initial_wealth
  	holdings = weights * total_wealth
  	wealthtracker = rep(0, n_days)
  	for(today in 1:n_days) {
  		return.today = resample(all_returns, 1, orig.ids=FALSE)
  		holdings = holdings + holdings*return.today
  		total_wealth = sum(holdings)
  		wealthtracker[today] = total_wealth
  		holdings = weights * total_wealth
  	}
  	wealthtracker
  }
  return(sim1)
}
```

### Hedge fund

**input symbols**

```{r, message=FALSE}
#input#######################
startdate = as.Date('2014-8-17')
mystocks = c("MNA", "FVC", "WTMF", "PUTW", "GMOM", "RLY", "BEMO", "CPI", "JPMF", "RYZZ")
##############################

getSymbols(mystocks)

#input######################################
mysymbols = list(MNA, FVC, WTMF, PUTW, GMOM, RLY, BEMO, CPI, JPMF, RYZZ)
############################################

# don't know how to append element if list, just pick symbols mannually
for(i in c(1:length(mysymbols))){
  print( paste(mystocks[[i]], min(index(mysymbols[[i]])) <= startdate))
}
```

**decide symbols**

```{r}
# pick symbols mannually ################################
usesymbols = list(MNA, FVC, WTMF, RLY, CPI)
usesymbolsnames = list("MNA", "FVC", "WTMF", "RLY", "CPI")
##########################################################
```

**pre-process data, ClCl, take a look**

```{r}
all_returns = get_allreturn(usesymbols)

# check if anything weried
head(all_returns)
pairs(all_returns)
```

**simulation**

```{r}
initial_wealth = 100000
n_days = 20
sim1 = get_sim1(all_returns=all_returns, initial_wealth = initial_wealth, n_days=n_days)
# Profit/loss
mean(sim1[,n_days])
hist(sim1[,n_days]- initial_wealth, breaks=30)
quantile(sim1[,n_days]- initial_wealth, .05)
```

### Real Estate

**input symbols**

```{r, message=FALSE}
#input#######################
startdate = as.Date('2014-8-17')
mystocks = c("VNQ",	"SCHH",	"IYR",	"XLRE",	"RWR",	"ICF",	"USRT",	"REM",	"FREL",	"REZ",	"BBRE")
##############################

getSymbols(mystocks)

#input######################################
mysymbols = list(VNQ,	SCHH,	IYR,	XLRE,	RWR,	ICF,	USRT,	REM,	FREL,	REZ,	BBRE)
############################################

# don't know how to append element if list, just pick symbols mannually
for(i in c(1:length(mysymbols))){
  print( paste(mystocks[[i]], min(index(mysymbols[[i]])) <= startdate))
}
```

**decide symbols**

```{r}
# pick symbols mannually ################################
usesymbols = list(VNQ, SCHH, IYR, RWR, ICF)
usesymbolsnames = list("VNQ", "SCHH", "IYR", "RWR", "ICF")
##########################################################
```

**pre-process data, ClCl, take a look**

```{r}
all_returns = get_allreturn(usesymbols)

# check if anything weried
head(all_returns)
pairs(all_returns)
```

```{r}
initial_wealth = 100000
n_days = 20
sim1 = get_sim1(all_returns=all_returns, initial_wealth = initial_wealth, n_days=n_days)
# Profit/loss
mean(sim1[,n_days])
hist(sim1[,n_days]- initial_wealth, breaks=30)
quantile(sim1[,n_days]- initial_wealth, .05)
```


### Stocks + fixed income 

**options from etfs from All Cap Equities ETFs**

IWR	IWS	VXF	ARKK	TILT

**options from Government Bonds ETFs**

SHV	IEF	SHY	TLT	GOVT

**make stock to fixed-income ratio as 3:2**


```{r, message=FALSE}
#input#######################
startdate = as.Date('2014-8-17')
mystocks = c("IWR",	"IWS",	"VXF",	"ARKK",	"TILT", "SHV",	"IEF",	"SHY",	"TLT",	"GOVT")
##############################

getSymbols(mystocks)

#input######################################
mysymbols = list(IWR,	IWS,	VXF,	ARKK,	TILT, SHV,	IEF,	SHY,	TLT,	GOVT)
############################################

# don't know how to append element if list, just pick symbols mannually
for(i in c(1:length(mysymbols))){
  print( paste(mystocks[[i]], min(index(mysymbols[[i]])) <= startdate))
}
```

**decide symbols**

```{r}
# pick symbols mannually ################################
usesymbols = list(IWR, IWS, VXF, SHV, IEF)
usesymbolsnames = list("IWR", "IWS", "VXF", "SHV", "IEF")
##########################################################
```


**pre-process data, ClCl, take a look**

```{r}
all_returns = get_allreturn(usesymbols)

# check if anything weried
head(all_returns)
pairs(all_returns)
```

```{r}
initial_wealth = 100000
n_days = 20
sim1 = get_sim1(all_returns=all_returns, initial_wealth = initial_wealth, n_days=n_days)
# Profit/loss
mean(sim1[,n_days])
hist(sim1[,n_days]- initial_wealth, breaks=30)
quantile(sim1[,n_days]- initial_wealth, .05)
```