---
title: "Question6 Association rule mining"
output: github_document
---

# Read data
Read data files and create transactions object.
```{r}
library(tidyverse)
library(arules)  # has a big ecosystem of packages built around it
library(arulesViz)

groceries = read.transactions("groceries.txt", sep=',')
summary(groceries)
```

# Generate rules
We try apriori algorithm with 0.01 support and 0.2 confidence. This choice will  drop rarer purchases, but weaker relationships will be kept.
```{r}
groceriesrules <- apriori(groceries,parameter=list(support=.01, confidence=.2, maxlen=10))

plot(groceriesrules, measure = c("support", "lift"), shading = "confidence")
plot(groceriesrules, measure = c("support", "confidence"), shading = "lift")
plot(groceriesrules, method='two-key plot')
```

# Choose a subset
Greater lift values indicate stronger associations. We choose the rule with a value greater than 2. The lift parameter ensures that very weak relationships are still dropped. At these levels, we see that a variety of grocery items--dairy, fruits, and meats--are associated with the purchase of root vegetables. Furthermore, we also see that buying any type of dairy (especially in conjunction with a produce item) is associated with buying another type. That's make sense in real life.
```{r}
subset_grule <- subset(groceriesrules, subset=lift > 2)
inspect(subset_grule)
plot(subset_grule, method='graph')
plot(head(subset_grule, 10, by='lift'), method='graph')
```